Models pretest

### 2022-12-07 Submission/Models_pretest.Rmd
highlighted

stargazer::stargazer(d1, d2, d3,
                     d4, d5, digits = 6,
                     no.space = TRUE,
                     title = "Logistic Regressions with president fixed-effects")

>>>>

stargazer::stargazer(d1, d2, d3,
                     d4, d5, digits = 3,
                     no.space = TRUE,
                     title = "Logistic Regressions with president fixed-effects",
                      column.sep.width = ".001pt",
                      font.size="small")
```
